---
title: ""
author: ""
date: ""
output: 
  md_document:
    variant: markdown_github
---

```{r,echo=FALSE,message=FALSE}
knitr::opts_chunk$set(fig.path="inst/img/README-", comment='.', message=FALSE)
```


# Calcium Bone Model

# Documentation
- Documentation [here](vignettes/modeldoc.Rmd)

# Installation
```{r,eval=FALSE}
remotes::install_github("metrumresearchgroup/cabone")
```

# Usage

- [Simulate teriparatide data](#teri)
- [Simulate denosumab data](#denos)
- [Simulate sclerostin mAb data](#scler)
- [Simulate secondary hyperparathyroidism](#hyper)
- [Simulate bone markers after sclerostin mAb](#scler2)


```{r,message=FALSE, warning=FALSE}
library(cabone)
library(ggplot2)
```


<a name="teri"></a>

## Simulate teriparatide data

- `PTHpm` teriparatide concentration (pM)
- `CaC` calcium concentration (mM)

```{r}
out <- sim_teri(dose=c(20,40), dur=9)

plot(out)
```


<a name="denos"></a>

### Simulate denosumab data

- `DENCP` denosumab concentration
- `BMDlsDENchange` lumbar spine change from basline


```{r}
out <- sim_denos(dose=c(10,60,210), dur=6)

plot(out, log(DENCP) + BMDlsDENchange ~ time, xlab="Time (months)")

```


<a name="scler"></a>

## Simulate sclerostin data 
```{r}
out <- sim_scler(dose=c(70,210,350), dur=12)

plot(out, SOSTCP + lsBMDsimSCLER ~ time, xlab="Time (hours)")

```

<a name="hyper"></a>

## Simulate secondary hyperparathyroidism

Have `GFR` decline by a certain amount (`GFRdelta`) over a 
certail period of time (`GFRtau`). 

- `CaC` calcium concentration 
- `PTHpm` parathyroid hormone 
- `GFR` glomerular filtration rate
- `OC` osteoclasts
- `ECCPhos` extracellular phosphate

All values are presented as fraction of the 
base line value.

```{r}
sim_2h() %>% plot
```


<a name="scler2"></a>

## Bone markers and BMD after sclerostin monoclonal antibody

- Re-create simulated data in Eudy, et al. (2015) CPT:PSP, figure 3

```{r}
sims <- sim_scler_data()
```

### `P1NP`
```{r}
ggplot(data=sims, aes(time,P1NPsim,col=label)) + 
   geom_line(lwd=1) + .colSet2()
```

### `CTX`
```{r}
ggplot(data=sims, aes(time,CTXsim,col=label)) + 
   geom_line(lwd=1)  + .colSet2()
```

### Lumbar spine `BMD`
```{r}
ggplot(data=sims, aes(time,lsBMDsimSCLER,col=label)) + 
   geom_line(lwd=1) + .colSet2()
```

### Total hip `BMD`
```{r}
ggplot(data=sims, aes(time,thBMDsimSCLER,col=label)) + 
   geom_line(lwd=1) + .colSet2()
```


## Teriparatide + denosumab combination therapy

```{r,eval=FALSE}
sims <- sim_combo_arms()
```


# Some helper functions

## Convert `teriparatide` doses

Usually, we think of doses in micrograms.  This function turns those
doses into `pmol`.

```{r}
amt_teri(20)
```

## Export the model code

It's a little hard to see what's happening here.  But basically, this grabs
the model code and writes it to a file of your choosing.  Use this when 
you want to export the model and start making changes yourself.

```{r}
file <- file.path(tempdir(),"my_model.cpp")
file_location <- cabone_export(file)
```


