---
title: ""
author: ""
date: ""
output: github_document
---

```{r,echo=FALSE,message=FALSE}
knitr::opts_chunk$set(fig.path="inst/img/README-", comment='.', message=FALSE)
```

# About
A multiscale systems model of bone function, remodeling and health. 

# Documentation
- Documentation [here](vignettes/modeldoc.Rmd)

# Installation
```{r,eval=FALSE}
remotes::install_github("metrumresearchgroup/cabone")
```

# Usage

- [Simulate teriparatide data](#teri)
- [Simulate denosumab data](#denos)



```{r,message=FALSE, warning=FALSE}
library(cabone)
library(ggplot2)
```


<a name="teri"></a>

## Simulate teriparatide data

- `PTHpm` teriparatide concentration (pM)
- `CaC` calcium concentration (mM)

```{r}
out <- sim_teri(dose=c(20,40), dur=9)

plot(out)
```


<a name="denos"></a>

### Simulate denosumab data

- `DENCP` denosumab concentration
- `BMDlsDENchange` lumbar spine change from basline


```{r}
out <- sim_denos(dose=c(10,60,210), dur=6)

plot(out, log(DENCP) + BMDlsDENchange ~ time, xlab="Time (months)")
```



# Some helper functions

## Convert `teriparatide` doses

Usually, we think of doses in micrograms.  This function turns those
doses into `pmol`.

```{r}
amt_teri(20)
```

## Export the model code

It's a little hard to see what's happening here.  But basically, this grabs
the model code and writes it to a file of your choosing.  Use this when 
you want to export the model and start making changes yourself.

```{r}
file <- file.path(tempdir(),"my_model.cpp")
file_location <- cabone_export(file)
```


