---
title: ""
author: ""
date: ""
output: 
  md_document:
    variant: markdown_github
---

```{r,echo=FALSE,message=FALSE}
knitr::opts_chunk$set(fig.path="inst/img/README-", comment='.', message=FALSE)
```


# Calcium Bone Model

## Documentation
- Documentation [here](vignettes/modeldoc.Rmd)

## Installation
```{r,eval=FALSE}
remotes::install_github("metrumresearchgroup/cabone")
```

## Usage
```{r,message=FALSE, warning=FALSE}
library(cabone)
```


## Simulate teriparatide data

```{r}
out <- sim_teri(dose=c(20,40), dur=9)

plot(out)
```

## Simulate denosumab data

```{r}
out <- sim_denos(dose=c(10,60,210), dur=6)

plot(out, log(DENCP) + BMDlsDENchange~time)
```

# Simulate secondary hyperparathyroidism

Have `GFR` decline by a certain amount (`GFRdelta`) over a 
certail period of time (`GFRtau`). 

```{r}
sim_2h() %>% plot
```


# Some helper functions

## Convert `teriparatide` doses

Usually, we think of doses in micrograms.  This function turns those
doses into `pmol`.

```{r}
amt_teri(20)
```

## Export the model code

It's a little hard to see what's happening here.  But basically, this grabs
the model code and writes it to a file of your choosing.  Use this when 
you want to export the model and start making changes yourself.

```{r}
file <- file.path(tempdir(),"my_model.cpp")
file_location <- cabone_export(file)
```


